Full Article Review

### 2024-08-15 doc/reviews/daniel.qmd
clean: the notes taken so far

- this paper is mostly about a database for sharing spinal injusry data. There are some points for how to improve sharing but not much about open collaboration
- open data commons for spinal injury
- Studies based on game theory suggest that data sharing might be beneficial if a collaborative approach is taken and data sharing is embraced as a community rather than by individuals
- key events for the collaboration to be possible: - introduction of FAIR principles, - update from funders, funding given to specific projects
- Open Data Commons for SCI (ODC-SCI, odc-sci.org), a platform to share tabular data of research in the field of spinal cord injury
- Ain of the paper: to illustrate how members of research communities can work together toward the development of dedicated data sharing initiatives under the umbrella of FAIR
- clearly highlighted the value of the massive demonstration/work for beta testing the site to reveal unforeseen problems
- Moreover, participants pointed out the need for improving self-explanatory tutorials and help materials that would facilitate the learning experience for those who could not attend the workshop
- “Registered users can request to become ODC-SCI Community members with further approval by the Leadership team.” The most permissive account type is becoming an ODC-SCI Community member associated to an ODC-SCI lab, known as a Lab member

@@

# Lessons Learned: A Neuroimaging Research Center’s Transition to Open and Reproducible Science

>>>>

-   this paper is mostly about a database for sharing spinal injusry
    data. There are some points for how to improve sharing but not much
    about open collaboration
-   open data commons for spinal injury
-   Studies based on game theory suggest that data sharing might be
    beneficial if a collaborative approach is taken and data sharing is
    embraced as a community rather than by individuals
-   key events for the collaboration to be possible: - introduction of
    FAIR principles, - update from funders, funding given to specific
    projects
-   Open Data Commons for SCI (ODC-SCI, odc-sci.org), a platform to
    share tabular data of research in the field of spinal cord injury
-   Ain of the paper: to illustrate how members of research communities
    can work together toward the development of dedicated data sharing
    initiatives under the umbrella of FAIR
-   clearly highlighted the value of the massive demonstration/work for
    beta testing the site to reveal unforeseen problems
-   Moreover, participants pointed out the need for improving
    self-explanatory tutorials and help materials that would facilitate
    the learning experience for those who could not attend the workshop
-   "Registered users can request to become ODC-SCI Community members
    with further approval by the Leadership team." The most permissive
    account type is becoming an ODC-SCI Community member associated to
    an ODC-SCI lab, known as a Lab member

@@

# Lessons Learned: A Neuroimaging Research Center's Transition to Open and Reproducible Science
